How do we copy and paste? The semantic drift of quotations in blogspace

### 2015-03-09 brains-protocol.tex
thoroughly validated RC1

\TB{We could therefore study the individual transformation process at work when authors alter quotations, by examining the modified words in each transformation.} To keep the analysis palatable, we focused on quotation transformations consisting in the \emph{substitution} of a word by another word (and only those cases) in order to unambiguously discuss single word replacements.
To quantify those substitutions, we decided to associate a number of features to each word, the variation of which we can statistically study.

@@

The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
{If we set aside the values for low Number of phonemes}, for each of these features it is indeed possible to draw a constant line which always remains within the respective confidence intervals.
If these variables have an effect, it is by no means as strong as it is for Word frequency.
This is remarkably clear for Clustering coefficient and Age of acquisition, where susceptibility values remain within quite small intervals (respectively $[.13-.18]$ and $[.16-.20]$).
{We may notice a slight effect for the lowest values of Number of synonyms and Number of phonemes, where the mean susceptibility is almost half as high as the average of the other values (respectively $.09$ vs. $.16$, and $.11$ vs. $.17$).}
Keeping in mind the poor statistical significance of this effect, we could still wonder if the shortest words and words with fewest synonyms are significantly less susceptible to substitution.
To further examine this phenomenon, we plotted the two-dimensional map of susceptibility values for these two features (see heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
%\TG{TBF: [[We see that outlier values (the two darkest cells) are both due to cells where the number of items is only slightly above the significance threshold (11 items, while we decided to cut at 10).]]}
%\TG{TBF: [[If we focus on cells based on at least several dozens of words]]}
\TB{Even if there are a few outlier cells, values tend to navigate around the mean value ($.16$) with little obvious regularity (except for a low number of synonyms, consistent with the unidimensional graph)}. {On the whole, this makes it relatively hard to draw any conclusion as regards the direction of an effect, except for the least populated value ranges (which as a result are also less significant).}
%\TG{TBF: [[This confirms the fact that the slight late increases observed for Age of acquisition and Number of phonemes are rather non-significant.]]}

@@

All in all, apart from Word frequency and despite some local tendencies, {in general} these results do not allow us to conclude \TB{\sout{either}} to a marked effect %or to no effect
of the selected psycholinguistic features on substitution susceptibility.
We may therefore globally assume that substitution targets are chosen in a more or less uniform way with respect to these features.

>>>>

{We could therefore study the individual transformation process at work when authors alter quotations, by examining the modified words in each transformation.} To keep the analysis palatable, we focused on quotation transformations consisting in the \emph{substitution} of a word by another word (and only those cases) in order to unambiguously discuss single word replacements.
To quantify those substitutions, we decided to associate a number of features to each word, the variation of which we can statistically study.

@@

The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
{If we set aside the values for low Number of phonemes}, for each of these features it is indeed possible to draw a constant line which always remains within the respective confidence intervals.
If these variables have an effect, it is by no means as strong as it is for Word frequency.
This is remarkably clear for Clustering coefficient and Age of acquisition, where susceptibility values remain within quite small intervals (respectively $[.13-.18]$ and $[.16-.20]$).
{We may notice a slight effect for the lowest values of Number of synonyms and Number of phonemes, where the mean susceptibility is almost half as high as the average of the other values (respectively $.09$ vs. $.16$, and $.11$ vs. $.17$).}
Keeping in mind the poor statistical significance of this effect, we could still wonder if the shortest words and words with fewest synonyms are significantly less susceptible to substitution.
To further examine this phenomenon, we plotted the two-dimensional map of susceptibility values for these two features (see heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
%\TG{TBF: [[We see that outlier values (the two darkest cells) are both due to cells where the number of items is only slightly above the significance threshold (11 items, while we decided to cut at 10).]]}
%\TG{TBF: [[If we focus on cells based on at least several dozens of words]]}
{Even if there are a few outlier cells, values tend to navigate around the mean value ($.16$) with little obvious regularity (except for a low number of synonyms, consistent with the unidimensional graph)}. {On the whole, this makes it relatively hard to draw any conclusion as regards the direction of an effect, except for the least populated value ranges (which as a result are also less significant).}
%\TG{TBF: [[This confirms the fact that the slight late increases observed for Age of acquisition and Number of phonemes are rather non-significant.]]}

@@

All in all, apart from Word frequency and despite some local tendencies, {in general} these results do not allow us to conclude to a marked effect %or to no effect
of the selected psycholinguistic features on substitution susceptibility.
We may therefore globally assume that substitution targets are chosen in a more or less uniform way with respect to these features.

### 2015-03-09 brainscopycut.tex
Phrasing fixes, blue text to validate
thoroughly validated RC1

@@

\title{How do we copy and paste? The semantic drift of quotations in blogspace}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE / USR 3130\\Friedrichstr 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE / USR 3130\\Friedrichstr 191, D-10117 Berlin}
\abstract{We describe reformulation processes within a large distributed system such as blogspace;
showing how some specific features of public representations may be altered by bloggers when they freely reproduce them.
To deal with robust and simple cultural representations, we focus on the evolution of quotations.
In particular, we uncover some of the semantic and structural characteristics of individual words and the substitutions they undergo.
Our work amounts to a large \emph{in vivo} experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
We show that all variables remarkably exhibit a single attractor and are generally contractile.
Even though the observed convergence patterns only partially explain quotation evolution, we shed light on a class of phenomena which are prone to constitute a key element of a broader empirically-grounded, attractor-based theory of cultural evolution.}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{word production; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; \emph{in vivo} psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

>>>>

% Strikethrough (with the \sout comment)
\usepackage[normalem]{ulem}

@@

\title{How do we copy and paste? The semantic drift of quotations in blogspace}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE\\Friedrichstr. 191, D-10117 Berlin}
\abstract{We describe reformulation processes within a large distributed system such as blogspace;
showing how some specific features of public representations may be altered by bloggers when they freely reproduce them.
To deal with robust and simple cultural representations, we focus on the evolution of quotations.
In particular, we uncover some of the semantic and structural characteristics of individual words and the substitutions they undergo.
Our work amounts to a large \emph{in vivo} experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
We show that all variables remarkably exhibit a single attractor and are generally contractile.
Even though the observed convergence patterns only partially explain quotation evolution, we shed light on a class of phenomena which are prone to constitute a key element of a broader empirically-grounded, attractor-based theory of cultural evolution.}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{word production; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; \emph{in vivo} psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}
